Empirical Analysis of Performance Bottlenecks in Graph Neural Network Training with GPUs

### 2020-12-21 NEUROC/sec4-experiments.tex
更新图片的宽度.

To verify the time complexity analysis in \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex}, we first compared the training time of the four GNNs.
%
The ranking of the training time was GaAN $\gg$ GAT $>$ GGNN $>$ GCN in all cases.
%
Since the real-world graphs had more edges than vertices ($|\mathcal{E}| > |\mathcal{V}|$), the time complexity of the edge calculation stage affected more than the vertex calculation stage.
%
The ranking was consistent with the time complexity analysis.

\begin{figure}[htb]
    \centering
    \subfloat[\texttt{pub}\label{fig:exp_absolute_training_time_pubmed}]{\includegraphics[height=4cm]{figs/experiments/exp_absolute_training_time_comparison_pubmed.pdf}}
    \subfloat[\texttt{aph}\label{fig:exp_absolute_training_time_amazon-photo}]{\includegraphics[height=4cm]{figs/experiments/exp_absolute_training_time_comparison_amazon-photo.pdf}}
    \subfloat[\texttt{cph}\label{fig:exp_absolute_training_time_coauthor-physics}]{\includegraphics[height=4cm]{figs/experiments/exp_absolute_training_time_comparison_coauthor-physics.pdf}} \\
    \subfloat[\texttt{amc}\label{fig:exp_absolute_training_time_amazon-computers}]{\includegraphics[height=4cm]{figs/experiments/exp_absolute_training_time_comparison_amazon-computers.pdf}}
    \subfloat[\texttt{fli}\label{fig:exp_absolute_training_time_flickr}]{\includegraphics[height=4cm]{figs/experiments/exp_absolute_training_time_comparison_flickr.pdf}}
    \subfloat[\texttt{cam}\label{fig:exp_absolute_training_time_com-amazon}]{\includegraphics[height=4cm]{figs/experiments/exp_absolute_training_time_comparison_com-amazon.pdf}}
    \caption{Distribution of the wall-clock training time of 50 epoches on different datasets. GaAN crashed due to out of memory exception on the \texttt{cph} dataset.}
    \label{fig:exp_absolute_training_time}
\end{figure}

To further evaluate effects of hyper-parameters on performance, we measured the training time of each GNN with varying hyper-parameters in \figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time}.

\begin{figure}[H]
    \centering
    \subfloat[GCN\label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gcn}]{\includegraphics[height=3cm]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gcn.pdf}}
    \\
    \subfloat[GGNN\label{fig:exp_hyperparameter_on_vertex_edge_phase_time_ggnn}]{\includegraphics[height=3cm]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_ggnn.pdf}}
    \\
    \subfloat[GAT\label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gat}]{\includegraphics[height=6cm]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gat.pdf}}
    \\
    \subfloat[GaAN\label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gaan}]{\includegraphics[height=6cm]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gaan.pdf}}

    \caption{Effects of hyper-parameters on the edge/vertex calculation time.}
    \label{fig:exp_hyperparameter_on_vertex_edge_phase_time}
\end{figure}

>>>>

To verify the time complexity analysis in \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex}, we first compared the training time of the four GNNs in \figurename~\ref{fig:exp_absolute_training_time}.
%
The ranking of the training time was GaAN $\gg$ GAT $>$ GGNN $>$ GCN in all cases.
%
Since the real-world graphs had more edges than vertices ($|\mathcal{E}| > |\mathcal{V}|$), the time complexity of the edge calculation stage affected more than the vertex calculation stage.
%
The ranking was consistent with the time complexity analysis.

\begin{figure}[htb]
    \centering
    \includegraphics[width=0.32\textwidth]{figs/experiments/exp_absolute_training_time_comparison_pubmed.pdf}
    \includegraphics[width=0.32\textwidth]{figs/experiments/exp_absolute_training_time_comparison_amazon-photo.pdf}
    \includegraphics[width=0.32\textwidth]{figs/experiments/exp_absolute_training_time_comparison_coauthor-physics.pdf}

    \includegraphics[width=0.32\textwidth]{figs/experiments/exp_absolute_training_time_comparison_amazon-computers.pdf}
    \includegraphics[width=0.32\textwidth]{figs/experiments/exp_absolute_training_time_comparison_flickr.pdf}
    \includegraphics[width=0.32\textwidth]{figs/experiments/exp_absolute_training_time_comparison_com-amazon.pdf}
    %\subfloat[\label{fig:exp_absolute_training_time_pubmed}]{\includegraphics[width=0.32\textwidth]{figs/experiments/exp_absolute_training_time_comparison_pubmed.pdf}}
    %\subfloat[\label{fig:exp_absolute_training_time_amazon-photo}]{\includegraphics[width=0.32\textwidth]{figs/experiments/exp_absolute_training_time_comparison_amazon-photo.pdf}}
    %\subfloat[\label{fig:exp_absolute_training_time_coauthor-physics}]{\includegraphics[width=0.32\textwidth]{figs/experiments/exp_absolute_training_time_comparison_coauthor-physics.pdf}} \\
    %\subfloat[\label{fig:exp_absolute_training_time_amazon-computers}]{\includegraphics[width=0.32\textwidth]{figs/experiments/exp_absolute_training_time_comparison_amazon-computers.pdf}}
    %\subfloat[\label{fig:exp_absolute_training_time_flickr}]{\includegraphics[width=0.32\textwidth]{figs/experiments/exp_absolute_training_time_comparison_flickr.pdf}}
    %\subfloat[\label{fig:exp_absolute_training_time_com-amazon}]{\includegraphics[width=0.32\textwidth]{figs/experiments/exp_absolute_training_time_comparison_com-amazon.pdf}}
    \caption{Distribution of the wall-clock training time of 50 epoches on different datasets. GaAN crashed due to out of memory exception on the \texttt{cph} dataset.}
    \label{fig:exp_absolute_training_time}
\end{figure}

To further evaluate effects of hyper-parameters on performance, we measured the training time of each GNN with varying hyper-parameters in \figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_gcn} to \figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_gaan}.

\begin{figure}[H]
    \centering
    \includegraphics[width=0.6\textwidth]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gcn.pdf}
    \caption{Effects of hyper-parameters on the vertex/edge calculation time of GCN.}
    \label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gcn}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.6\textwidth]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_ggnn.pdf}
    \caption{Effects of hyper-parameters on the vertex/edge calculation time of GGNN.}
    \label{fig:exp_hyperparameter_on_vertex_edge_phase_time_ggnn}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.6\textwidth]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gat.pdf}
    \caption{Effects of hyper-parameters on the vertex/edge calculation time of GGNN.}
    \label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gat}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.9\textwidth]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gaan.pdf}
    \caption{Effects of hyper-parameters on the vertex/edge calculation time of GaAN.}
    \label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gaan}
\end{figure}

%\begin{figure}[H]
    %\centering
    %\subfloat[GCN\label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gcn}]{\includegraphics[width=0.6\textwidth]%{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gcn.pdf}}
%    \\
    %\subfloat[GGNN\label{fig:exp_hyperparameter_on_vertex_edge_phase_time_ggnn}]{\includegraphics[width=0.6\textwidth]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_ggnn.pdf}}
%    \\
    %\subfloat[GAT\label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gat}]{\includegraphics[width=0.6\textwidth]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gat.pdf}}
    %\\
    %\subfloat[GaAN\label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gaan}]{\includegraphics[width=0.9\textwidth]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gaan.pdf}}

    %\caption{Effects of hyper-parameters on the edge/vertex calculation time.}
    %\label{fig:exp_hyperparameter_on_vertex_edge_phase_time}
%\end{figure}
